Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-02-14 manuscript.Rmd
updated data files for paper
figuring out better select model

## Goal 1: Optimize and validate body position classification model
<!--resampled-metrics, splithalf-metrics, predictions CSVs generated from tune_ml/classification_tidymodels.R -->
```{r}
metrics_rs <- read_csv("data/resampled-metrics.csv") 
metrics_sp <- read_csv("data/splithalf-metrics.csv")

@@

## Goal 2: Assess classification accuracy over long recordings
<!-- compiled_agreement.csv, generated from analysis-pt2/compile_agreement.R -->

>>>>

## Goal 1: Optimize and validate body position classification model
<!-- group_split_metrics, generated from group_split_comparison in this proj, stable copy in data/ -->
```{r}
metrics <- read_csv("data/group_split_metrics.csv")

@@

## Goal 2: Assess classification accuracy over long recordings
<!-- compiled_agreement, generated from analysis-part2 -->

```{r}
